Online Multiclass Linear Classification with Bandit Feedback

### 2018-12-18 arxiv-version/main.tex
Fixes

We design new algorithms for the problem of \textsc{Online Multiclass
Classification with Bandit Feedback}. In this problem, in each round, the
algorithm receives a feature vector and the algorithm has to predict one of $K$
possible classes. Immediately after the algorithm makes its prediction, it
receives feedback whether the prediction was correct or not. However, in
contrast with the standard, so called full information setting, the algorithm
does \emph{not} receive the correct label. The feedback is only binary. To allow
for meaningful use of randomization, we assume that the correct label in a
particular round is chosen prior to algorithm's prediction in that
round.\footnote{The reader can assume throughout the paper a simpler model of
the so called \emph{oblivious adversary} where the whole sequence of labeled
examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
round of the game.} The protocol of the problem is stated below.

@@

The goal is to design an algorithm that makes small number of mistakes
$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The problem
was initially proposed by \cite{Kakade-Shalev-Shwartz-Tewari-2008}. The
corresponding problem with full information feedback is solved by the classical
\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The problem is quite
natural and potential applications include online advertising and online content
optimization where the feedback corresponds to a user's click.

@@

For the standard notion of linear separability, we propose several algorithms
with various time-complexity-versus-mistake-bound trade-offs. First class of
algorithms map the examples into a high-dimensional inner product space. In this
space the examples become \emph{strongly} linearly separable. This allows us to
run the algorithm for the strongly linearly separable case. All of these
algorithms can be kernelized. (Some of them have to be kernalized since the
underlying inner product space is infinite dimensional.) Kernelization does not
change the input-output behavior of the algorithm, it only affects its time
complexity.

These algorithms differ by choice of the mapping or, equivalently, choice of the
kernel. The crux of the problem is the analysis of the approximation properties
of these mappings/kernels and the way margin in original space under standard
linear separability notion gets transformed into a margin in the
high-dimensional space under the strong separability notion. This problem is
related to the problem of learning intersection of halfspaces and has been
studied previously by \cite{Klivans-Servedio-2008}. As an important technical
achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
removing completely the dependency on the original dimension $d$.

@@

The notion of linear separability with a margin is standard. It used in the
full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
folklore result that if a set of labeled examples is separable with a margin
$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
essentially optimal in the sense that any deterministic algorithm must make
$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
completeness, we give proofs of both of these results in
Section~\ref{section:multiclass-perceptron-proofs}.

@@

The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
Perceptron} algorithm. Each copy corresponds to a class. In each round, each
copy makes a binary decision whether the feature vector belongs its respective
class or not. If at least one copy makes a positive prediction, the algorithm
predicts accordingly. If multiple copies make positive predictions, the
algorithm chooses one of them arbitrarily. If all copies make negative
predictions, the algorithms makes a blind guess.

\begin{algorithm}[h]
\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t \in V$}
\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\ENDIF
\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$S_t = \emptyset$}
\IF{$z_t = 1$}
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
\ENDIF
\ELSE
\IF{$z_t = 1$}
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
\ELSE
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Mistake upper bound]
\label{theorem:strongly-separable-example-mistake-upper-bound}
Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
integer, $\gamma$ a positive real number, $R$ be a non-negative real number. If
$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then the
expected number of mistakes
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$.
\end{theorem}

@@

Let $C$ be the number of times line 16 gets executed. Let $U$ be the number of
times line 16 and line 21 get executed. In other words, $U$ is the number of
times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
updated. Clearly, $U = A + C$.

@@

To finish the proof, we need to upper bound the number of updates, $U$. We claim
that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2} and
\eqref{equation:strong-linear-separability-3}.
The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
changes only if there is an update in round $t$.
We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
we have
\begin{align*}
\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
\end{align*}
Therefore, after $U$ updates,
$$
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
$$
Similarly, if there is an update in round $t$, we have
\begin{align*}
\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma
\end{align*}
where the last inequality follows from \eqref{equation:strong-linear-separability-2}
and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
Thus, after $U$ updates,
$$
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma U \; .
$$
Applying Cauchy-Schwartz's inequality twice and assumption
\eqref{equation:strong-linear-separability-1}, we get that
$$
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
$$
Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
$$
(\gamma U)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
$$
We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
\end{proof}

@@

In this section, we show how construct a mapping $\phi$ of points in the unit
ball of $\R^d$ into a high dimensional inner product space that has the
property if any set of labeled examples in the unit ball is linearly separable with a
margin $\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
the number of classes $K$, and the are specified in the theorems below.

@@

The proofs of the theorems can be found in
Section~\ref{section:proof-of-polynomial-approximation}. The geometric
interpretation of the two regions described in parts 1 and 2 of the theorems is
explained in Figure~\ref{figure:pizza-slice}.

>>>>

We design new algorithms for the problem of \textsc{Online Multiclass
Classification with Bandit Feedback}. In this problem, in each round, the
algorithm receives a feature vector and the algorithm has to predict one of $K$
possible classes. Immediately after the algorithm makes its prediction, it
receives feedback whether the prediction was correct or not. However, in
contrast with the standard, so called full information setting, the algorithm
does \emph{not} receive the correct label. The feedback is only binary. To allow
for meaningful use of randomization, we assume that the correct label in a
particular round is chosen prior to algorithm's prediction in that
round.\footnote{All our results apply to also to a simpler model of
the so called \emph{oblivious adversary} where the whole sequence of labeled
examples $(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is chosen before the first
round of the game.} The protocol of the problem is stated below.

@@

The goal is to design an algorithm that makes small number of mistakes
$\sum_{t=1}^T z_t = \sum_{t=1}^T \indicator{\widehat y_t \neq y_t}$. The problem
was initially proposed by \cite{Kakade-Shalev-Shwartz-Tewari-2008}. The
corresponding problem with full information feedback is solved by the classical
\textsc{Multiclass Perceptron} algorithm and its variants (see e.g.
\cite{Crammer-Dekel-Keshet-Shalev-Shwartz-Singer-2006}). The bandit feedback
version is a mathematically natural model and potential applications include
online advertising and online content optimization where the binary feedback
corresponds to a click.

@@

For the standard notion of linear separability, we propose several algorithms
with various time-complexity-versus-mistake-bound trade-offs. First class of
algorithms map the examples into a high-dimensional inner product space. In this
space the examples become \emph{strongly} linearly separable. This allows us to
run the algorithm for the strongly linearly separable case. All of these
algorithms can be kernelized. (Some of them have to be kernalized since the
underlying inner product space is infinite dimensional.) Kernelization does not
change the input-output behavior of the algorithm, it only affects its time
and memory complexity.

These algorithms differ by choice of the mapping or, equivalently, choice of the
kernel. The crux of the problem is the analysis of the approximation properties
of these mappings/kernels and the way margin in the original space $\R^d$ under
standard linear separability notion gets transformed into a margin in the
high-dimensional space under the strong separability notion. This problem is
related to the problem of learning intersection of halfspaces and has been
studied previously by \cite{Klivans-Servedio-2008}. As an important technical
achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
removing completely the dependency on the original dimension $d$.

@@

The notion of linear separability with a margin is standard. It used in the
full-information setting to upper bound the number of mistakes of the
\textsc{Multiclass Perceptron} algorithm. For completeness, we state the
algorithm in Appendix~\ref{section:multiclass-perceptron-proofs}. It is a
folklore result that if a set of labeled examples is separable with a margin
$\gamma$ and the norm of the examples is bounded by $R$ then \textsc{Multiclass
Perceptron} algorithm makes at most $\left\lfloor 2(R/\gamma)^2 \right \rfloor$
mistakes. Another folklore result is that \textsc{Multiclass Perceptron} is
essentially optimal in the sense that any deterministic algorithm must make
$\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. For
completeness, we give proofs of both of these results in
Appendix~\ref{section:multiclass-perceptron-proofs}.

@@

The idea behind the algorithm is to use $K$ copies of the \textsc{Binary
Perceptron} algorithm. Each copy corresponds to a class. In each round, each
copy makes a binary decision whether the feature vector belongs its respective
class or not. If at least one copy makes a positive prediction, the algorithm
predicts accordingly. If multiple copies make positive predictions, the
algorithm chooses one of them arbitrarily. If all copies make negative
predictions, the algorithms makes a uniformly random guess.

\begin{algorithm}[h]
\caption{\textsc{Bandit Algorithm for Strongly Linearly Separable Examples}
\label{algorithm:algorithm-for-strongly-linearly-separable-examples}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$. Number of rounds $T$. Inner product space $(V,\ip{\cdot}{\cdot})$.}
\STATE{Initialize $w_1^{(1)} = w_2^{(1)} = \dots = w_K^{(1)} = 0$}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t \in V$}
\STATE{Compute $S_t = \left\{ i ~:~ 1 \le i \le K, \ \ip{w_i^{(t)}}{x_t} \ge 0 \right\}$}
\IF{$S_t = \emptyset$}
\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ELSE
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} + x_t$}
\ENDIF
\ELSE
\STATE{Predict $\widehat y_t \in S_t$ chosen arbitrarily}
\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \indicator{\widehat y_t \neq y_t}$}
\IF{$z_t = 1$}
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}$}
\STATE{Update $w_{\widehat y_t}^{(t+1)} = w_{\widehat y_t}^{(t)} - x_t$}
\ELSE
\STATE{Set $w_i^{(t+1)} = w_i^{(t)}$ for all $i \in \{1,2,\dots,K\}$}
\ENDIF
\ENDIF
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

\begin{theorem}[Mistake upper bound]
\label{theorem:strongly-separable-example-mistake-upper-bound}
Let $(V, \ip{\cdot}{\cdot})$ be any inner product space, let $K$ be a positive
integer, let $\gamma$ a positive real number, let $R$ be a non-negative real number. If
$(x_1, y_1), (x_2, y_2), \dots, (x_T, y_T)$ is a sequence of labeled examples in
$V \times \{1,2,\dots,K\}$ such that the examples are strongly separable with
margin $\gamma$ and $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$ then the
expected number of mistakes
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples}
makes is at most $(K-1) \lfloor (R/\gamma)^2 \rfloor$.
\end{theorem}

@@

Let $C$ be the number of times line 12 gets executed. Let $U$ be the number of
times line 12 and line 19 get executed. In other words, $U$ is the number of
times the $K$-tuple of vectors $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$ gets
updated. Clearly, $U = A + C$.

@@

To finish the proof, we need to upper bound the number of updates, $U$. We claim
that $U \le \lfloor (R/\gamma)^2 \rfloor$. The proof of this upper bound is
similar to the proof of the mistake bound for \textsc{Multiclass Perceptron}
algorithm. Let $w_1^*, w_2^*, \dots, w_K^* \in V$ be vectors that satisfy
\eqref{equation:strong-linear-separability-1},
\eqref{equation:strong-linear-separability-2} and
\eqref{equation:strong-linear-separability-3}.
The $K$-tuple $(w_1^{(t)}, w_2^{(t)}, \dots, w_K^{(t)})$
changes only if there is an update in round $t$.
We investigate how $\sum_{i=1}^K \norm{w_i^{(t)}}^2$ and
$\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}$ change. If there is an update in round $t$,
we have
\begingroup
\allowdisplaybreaks
\begin{align*}
\sum_{i=1}^K \norm{w_i^{(t+1)}}^2
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t+1)}}^2 \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \norm{w_i^{(t)}}^2 \right) + \norm{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t}^2 \\
& = \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 + \underbrace{(-1)^{z_t} 2 \ip{w_{\widehat y_t}^{(t)}}{x_t}}_{\le 0} \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + \norm{x_t}^2 \\
& \le \left( \sum_{i=1}^K \norm{w_i^{(t)}}^2 \right) + R^2 \; .
\end{align*}
\endgroup
Therefore, after $U$ updates,
$$
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
$$
Similarly, if there is an update in round $t$, we have
\begin{align*}
\sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}}
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \gamma
\end{align*}
where the last inequality follows from \eqref{equation:strong-linear-separability-2}
and \eqref{equation:strong-linear-separability-3} and analysis of the cases $z_t = 0$ and $z_t = 1$.
Thus, after $U$ updates,
$$
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}} \ge \gamma U \; .
$$
Applying Cauchy-Schwartz's inequality twice and assumption
\eqref{equation:strong-linear-separability-1}, we get that
$$
\sum_{i=1}^K \ip{w_i^*}{w_i^{(T+1)}}
\le \sum_{i=1}^K \norm{w_i^*} \cdot \norm{w_i^{(T+1)}}
\le \sqrt{\sum_{i=1}^K \norm{w_i^*}^2} \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2}
\le \sqrt{\sum_{i=1}^K \norm{w_i^{(T+1)}}^2} \; .
$$
Combining the upper and lower bounds on $\sum_{i=1}^K \norm{w_i^{(T+1)}}^2$ inequalities, we get
$$
(\gamma U)^2 \le \sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
$$
We conclude that $U \le (R/\gamma)^2$. Since $U$ is an integer, $U \le \lfloor (R/\gamma)^2 \rfloor$.
\end{proof}

The upper bound $(K-1) \lfloor (R/\gamma)^2 \rfloor$ on the expected number of
mistakes of
Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples} is
optimal to within constant factor as long as the number of classes $K$ is
at most $O((R/\gamma)^2)$. This is proved in
\autoref{theorem:strongly-separable-example-mistake-lower-bound} below.

Irrespective of any conditions on $K$, $R$, and $\gamma$, a trivial lower bound
on the expected number of mistakes of any randomized algorithm is
$\frac{K-1}{2}$. (Adversary chooses the same example over and over.) However, it
is unclear if the trivial lower bound is the best possible if $K$ is large,
i.e., $\omega((R/\gamma)^2)$. We leave this as an open problem.

@@

In this section, we show how to construct a mapping $\phi$ from the unit
ball of $\R^d$ into a high dimensional inner product space that has the
property if a set of labeled examples in the unit ball is linearly separable with a
margin $\gamma$, applying the mapping $\phi$ makes the examples \emph{strongly}
linearly separable with a margin $\gamma'$ and their norms are bounded by $R'$.
The parameters $\gamma'$ and $R'$ are functions of the old margin $\gamma$ and
the number of classes $K$, and the are specified in the theorems below.

@@

The proofs of the theorems can be found in
Section~\ref{section:proof-of-polynomial-approximation}. The geometric
interpretation of the two regions described in parts 1 and 2 of the theorems is
explained in Figure~\ref{figure:pizza-slice}. Similar but weaker results were
proved by~\cite{Klivans-Servedio-2008}. In particular, we prove that the degrees
of the polynomials, their norms, and their ``margins'' (parts 1 and 2 of theorems)
are independent of the dimension $d$.
